Social Computing Article\thanks{This title is temporary}

### 2013-01-23 Article.tex
Dei um jeito nas referências e retirei a imagem do sudoku do artigo
Incluí os novos gráficos das Gaussianas e falei sobre eles nos resultados

We have consistent evidence that trial-and-error is a part of the {\em Sudoku} solving experience. The need for trial-and-error in {\em Sudoku} puzzles is not a falsifiable conclusion, but a mathematical fact~\cite{davis:mathsudoku}. Some puzzles are only solvable by the means of a backtracking procedure (see Figure~\ref{fig:trial_and_error_sudoku}).

\begin{figure}
\includegraphics[scale=0.30]{trial_and_error_sudoku}
\caption{A {\em Sudoku} puzzle solvable only by trial-and-error}
\label{fig:trial_and_error_sudoku}
\end{figure}

@@

\subsection{Evaluating the Neighbours' Solutions is Beneficial to the Algorithm's Performance}

@@

As can be seen in Figure~\ref{fig:progression}, our experiments have shown that evaluating the proposed solutions indeed brings significantly better results, despite the fact that humans seemingly avoid that strategy~\cite{farenzena:collabem}. In all topologies, choosing the solution with the largest number of filled cells not only allows agents to solve the instance earlier, but also causes the network to converge faster to the correct solution. That is, once one individual has found the correct solution, that solution spreads faster through the network if the other agents are evaluating the solutions that reach them instead of copying an arbitrary one.

The strategy based on the behaviour observed in humans fared roughly the same as choosing a random neighbour to copy, and both underperformed in comparison to evaluating the solutions according to number of filled cells. This confirms that choosing solutions arbitrarily without taking their content into consideration is prejudicial to the process of social problem-solving.

Even so, that behaviour has been observed in human networks. In~\cite{farenzena:collabem} the authors suggest that it is justified in the real world because "in a non-virtual environment, the feedback of the environment can cause an agent to stop communicating, e.g. in the case of injury or death", so there would be no need for an agent to evaluate solutions because the environment is already selecting against ineffective ones. Since neither the original experiments nor our simulation included such a mechanism of natural selection, the advantages of that process have not been observed, but they might already be good enough that it would be unnecessary for the agents to have to spend effort evaluating the solutions.

@@

The limitation on the network's degree suggested by~\cite{farenzena:collabem} and employed by~\cite{mason:collablearnet} is also promising, and displays evidence of success. Fewer connections allows for all neighbours to be displayed in the interface at once, without necessity of effort by the user by clicking buttons or scrolling. Moreover, humans might feel more encouraged to evaluate their neighbours if the number of possible solutions is limited.

\begin{figure}
\includegraphics[scale=0.45]{progression}
\caption{Progression of the solution. The graph shows how many agents have successfully solved the puzzle in a given iteration (scale-free topology)
}
\label{fig:progression}
\end{figure}

>>>>

We have consistent evidence that trial-and-error is a part of the {\em Sudoku} solving experience. The need for trial-and-error in {\em Sudoku} puzzles is not a falsifiable conclusion, but a mathematical fact~\cite{davis:mathsudoku}. Some puzzles are only solvable by the means of a backtracking procedure.

@@

\begin{figure}
\includegraphics[scale=1]{ijcai_sudoku/ring}
\caption{Progression of the solution. The graph shows how many agents have successfully solved the puzzle in a given iteration (scale-free topology)}
\label{fig:ring_gauss}
\end{figure}

\begin{figure}
\includegraphics[scale=1]{ijcai_sudoku/sf}
\caption{Progression of the solution. The graph shows how many agents have successfully solved the puzzle in a given iteration (scale-free topology)}
\label{fig:sf_gauss}
\end{figure}

\begin{figure}
\includegraphics[scale=1]{ijcai_sudoku/geral}
\caption{Progression of the solution. The graph shows how many agents have successfully solved the puzzle in a given iteration (scale-free topology)}
\label{fig:global_gauss}
\end{figure}

\subsection{Evaluating Neighbours' Solutions is Advantageous even with an Inexact Metric}

@@

%%As can be seen in Figure~\ref{fig:progression}, 
Our experiments have shown that evaluating the proposed solutions indeed brings significantly better results, despite the fact that humans seemingly avoid that strategy~\cite{farenzena:collabem}. In all topologies, choosing the solution with the largest number of filled cells not only allows agents to solve the instance earlier, but also causes the network to converge faster to the correct solution. That is, once one individual has found the correct solution, that solution spreads faster through the network if the other agents are evaluating the solutions that reach them instead of copying an arbitrary one.

The strategy based on the behaviour observed in humans fared roughly the same as choosing a random neighbour to copy. That is to be expected because the position of each neighbour is already randomized, so there is virtually no difference between picking one of the first neighbours to copy and a random one among all. Seeing as the same conclusions apply to both the human and random strategies, we omit further analysis of the latter for simplicity. Both underperformed in comparison to evaluating the solutions according to number of filled cells. This confirms that choosing solutions arbitrarily without taking their content into consideration is prejudicial to the process of social problem-solving.

We have observed in our experiments that the progress of the solution, represented by the number of agents that solve the problem in a given iteration, follows a normal distribution. During the first few iterations no agents have found the solution. Then, in a moment that varies according to the particular instance of the problem, the first few agents solve the problem. From that point onwards the solution starts spreading through the network. As more agents obtain the complete solution, more likely it becomes that further agents will copy that solution from their neighbours, according to the conformist behaviour observed in~\cite{farenzena:collabem}. That leads the number of agents to obtain the solution to progressively increase in the following iterations, until it reaches a point where the few remaining agents take longer to obtain the solution due to factors such as being less capable solvers or being in unfavourable positions in the topology.

We have run experiments in the four different topologies enumerated above, for 7 different problem instances, and obtained similar results in each. The progression of the solution for the \emph{Most Filled} and \emph{First Positions} strategies can be described as normal distributions of different mean and variance. In the context of the experiments, the mean indicates how soon the correct solution was found, and the variance how long it took to spread through the network. The exact values for those parameters vary widely according to factors such as topology and problem instance, but they follow a particular pattern. For all cases, the strategy that evaluated solutions had lower mean, indicating the solution was found sooner, and lower variance, meaning it spread faster. We have chosen the scale-free and 3-ring topologies as representative examples, and plotted the average of the results for a same instance of the problem for each in Figures~\ref{fig:sf_gauss} and~\ref{fig:ring_gauss}, respectively. In each can be seen the percentage of agents that find the correct solution in each iteration for the two strategies, with normal curves plotted over the values, evidencing the described behaviour. It's noticeable that the results fluctuate more for the second strategy, which is explained by its practically random method of choosing solutions to copy.

In Figure~\ref{fig:global_gauss} the average for all experiments can be seen, encompassing every topology and instance. In this graph, the presence of the normal behaviour in the distribution is less clear, due to it combining several different instances and topologies. Nevertheless, its effects can still be seen. The \emph{Most Filled} strategy displays different residual peaks from particular instances, while the line for the \emph{First Positions} strategy starts flattening with the accumulation of several distributions from the individual experiments. Most importantly, the general result of a sooner finding and faster spreading of the correct solution for the first strategy endures, showing its consistency over different scenarios.

Still, even though choosing a solution based on position instead of content is provably inefficient, that behaviour has been observed in human networks. In~\cite{farenzena:collabem} the authors suggest that it is justified in the real world because ``in a non-virtual environment, the feedback of the environment can cause an agent to stop communicating, e.g. in the case of injury or death'', so there would be no need for an agent to evaluate solutions because the environment is already selecting against ineffective ones. Since neither the original experiments nor our simulation included such a mechanism of natural selection, the advantages of that process have not been observed, but they might already be good enough that it would be unnecessary for the agents to have to spend effort evaluating the solutions.

@@

The limitation on the network's degree suggested by~\cite{farenzena:collabem} and employed by~\cite{mason:collablearnet} is also promising, and displays evidence of success. Fewer connections allows for all neighbours to be displayed in the interface at once, without necessity of effort by the user by clicking buttons or scrolling. Moreover, humans might feel more encouraged to evaluate their neighbours if the number of possible solutions is limited.
%
%\begin{figure}
%\includegraphics[scale=0.45]{progression}
%\caption{Progression of the solution. The graph shows how many agents have successfully solved the puzzle in a given iteration (scale-free topology)
%}
%\label{fig:progression}
%\end{figure}
